# Windrose Quarterly Figures
  
A wind rose visualizes the frequency of winds blowing from a specific direction of a desired Date Range. The data used for this figure were collected via the `rnoaa` R Package at station CDRF1 (Cedar Key, Florida). The legend represents the wind speed ranging from low (2-4 m/s) to high (18-20 m/s) wind speeds. The cardinal directions on the outer part of the wind rose indicate the direction of the wind. The Frequency is displayed as the lowest to highest percentage frequency of a wind speed occuring in a given direction, by the size of the wind magnitude polygon. Wind data are updated periodically through USGS (monthly basis).   
  
  
```{r windrose_options, setup, include=FALSE, warning=FALSE, message=FALSE, comment=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
options(dplyr.summarise.inform = FALSE)
library("lubridate")
library("ncdf4")
library("rnoaa")
library("RColorBrewer")
library("scales")
```


```{r, include= FALSE}
#wind17 <- buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2017)
#wind18 <- buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2018)
#wind19 <- buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2019)
wind20 <- buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2020)
wind21 <- buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2021)
wind <- rbind(wind20$data, wind21$data) %>% dplyr::distinct()

# Shrink the wind table, and convert the format of time
wind$time <- ymd_hms(wind$time)
    
plot.windrose <- function(data,
                              spd,
                              dir,
                              spdres = 2,
                              dirres = 22.5,
                              spdmin = 2,
                              spdmax = 20,
                              spdseq = NULL,
                              palette = "YlGnBu",
                              countmax = NA,
                              debug = 0){
      
      
      # Look to see what data was passed in to the function
      if (is.numeric(spd) & is.numeric(dir)){
        # assume that we've been given vectors of the speed and direction vectors
        data <- data.frame(spd = spd,
                           dir = dir)
        spd = "spd"
        dir = "dir"
      } else if (exists("data")){
        # Assume that we've been given a data frame, and the name of the speed 
        # and direction columns. This is the format we want for later use.    
      }  
      
      # Tidy up input data ----
      n.in <- NROW(data)
      dnu <- (is.na(data[[spd]]) | is.na(data[[dir]]))
      data[[spd]][dnu] <- NA
      data[[dir]][dnu] <- NA
      
      # figure out the wind speed bins ----
      if (missing(spdseq)){
        spdseq <- seq(spdmin,spdmax,spdres)
      } else {
        if (debug >0){
          cat("Using custom speed bins \n")
        }
      }
      # get some information about the number of bins, etc.
      n.spd.seq <- length(spdseq)
      n.colors.in.range <- n.spd.seq - 1
      
      # create the color map
      spd.colors <- colorRampPalette(brewer.pal(min(max(3,
                                                        n.colors.in.range),
                                                    min(9,
                                                        n.colors.in.range)),                                               
                                                palette))(n.colors.in.range)
      
      if (max(data[[spd]],na.rm = TRUE) > spdmax){    
        spd.breaks <- c(spdseq,
                        max(data[[spd]],na.rm = TRUE))
        spd.labels <- c(paste(c(spdseq[1:n.spd.seq-1]),
                              '-',
                              c(spdseq[2:n.spd.seq])),
                        paste(spdmax,
                              "-",
                              max(data[[spd]],na.rm = TRUE)))
        spd.colors <- c(spd.colors, "grey50")
      } else{
        spd.breaks <- spdseq
        spd.labels <- paste(c(spdseq[1:n.spd.seq-1]),
                            '-',
                            c(spdseq[2:n.spd.seq]))    
      }
      data$spd.binned <- cut(x = data[[spd]],
                             breaks = spd.breaks,
                             labels = spd.labels,
                             ordered_result = TRUE)
      
      # figure out the wind direction bins
      dir.breaks <- c(-dirres/2,
                      seq(dirres/2, 360-dirres/2, by = dirres),
                      360+dirres/2)  
      dir.labels <- c(paste(360-dirres/2,"-",dirres/2),
                      paste(seq(dirres/2, 360-3*dirres/2, by = dirres),
                            "-",
                            seq(3*dirres/2, 360-dirres/2, by = dirres)),
                      paste(360-dirres/2,"-",dirres/2))
      # assign each wind direction to a bin
      dir.binned <- cut(data[[dir]],
                        breaks = dir.breaks,
                        ordered_result = TRUE)
      levels(dir.binned) <- dir.labels
      data$dir.binned <- dir.binned
      
      # Run debug if required ----
      if (debug>0){    
        cat(dir.breaks,"\n")
        cat(dir.labels,"\n")
        cat(levels(dir.binned),"\n")
        
      }  
      
      
      # Create the labels:
      x_location <- pi # x location of the labels
      
      # Get the percentage
      T_data <- data %>%
        dplyr::group_by(dir.binned) %>%
        dplyr::summarise(count= n()) %>%
        dplyr::mutate(y = count/sum(count))
      
      labels <- data.frame(x = x_location,
                           y = scales::extended_breaks()(range(T_data$y)))
      
      
      # create the plot ---
      
      p.windrose <- ggplot() +
        geom_bar(data = data,
                 aes(x = dir.binned, y = (..count..)/sum(..count..),
                     fill = spd.binned))+
        geom_text(data = labels,
                  aes(x=x, y=y, label = scales::percent(y, 1))) +
        scale_y_continuous(breaks = waiver(),labels=NULL)+
        scale_x_discrete(drop = FALSE,
                         labels = c("N","NNE","NE","ENE", "E", 
                                    "ESE", "SE","SSE", 
                                    "S","SSW", "SW","WSW", "W", 
                                    "WNW","NW","NNW")) +
        ylab("")+xlab("")+
        coord_polar(start = -((dirres/2)/360) * 2*pi) +
        scale_fill_manual(name = "Wind Speed (m/s)", 
                          values = spd.colors,
                          drop = FALSE) +
        theme(axis.title.x = element_blank(),
              axis.text = element_text(size=13, face= "bold"), 
              axis.title = element_text(size=13, face= "bold"),
              legend.text = element_text(size = 12),
              axis.text.y=element_blank(),
              axis.ticks.y=element_blank())
      
      
      # adjust axes if required
      if (!is.na(countmax)){
        p.windrose <- p.windrose +
          ylim(c(0,countmax))
      }
      
      # print the plot
      print(p.windrose)  
      
      # return the handle to the wind rose
      return(p.windrose)
    }
```


```{r, include= FALSE}
wind0 <- wind %>%
  filter(time >= "2020-12-01 00:00:00" & time <= "2020-12-31 00:00:00") %>%
  select(time, wind_spd, wind_dir)

wind1 <- wind %>%
  filter(time >= "2021-01-01 00:00:00" & time <= "2021-01-31 00:00:00") %>%
  select(time, wind_spd, wind_dir)


wind2 <- wind %>%
  filter(time >= "2021-02-01 00:00:00" & time <= "2021-02-28 00:00:00") %>%
  select(time, wind_spd, wind_dir)
```

Windrose from December 1, 2020 to December 31, 2020
```{r, echo= FALSE}
dec_plot<-plot.windrose(spd = wind0$wind_spd,
                         dir = wind0$wind_dir)

```


Windrose from Janauary 1, 2021 to January 31, 2021
```{r, echo= FALSE}


jan_plot<-plot.windrose(spd = wind1$wind_spd,
                    dir = wind1$wind_dir)

```

Windrose from February 1, 2021 to February 28, 2021
```{r, echo= FALSE}


feb_plot<-plot.windrose(spd = wind2$wind_spd,
                          dir = wind2$wind_dir)

```


