# Landings  
  
This data set is manually updated by the oyster landings data located here: https://public.myfwc.com/FWRI/PFDM/ReportCreator.aspx.  The Commercial Fisheries Landings Summaries allows the user to select the date year range and oysters (as the Species).  

The Suwannee counties used in these figures are TAYLOR, DIXIE, and LEVY.  
The Apalachicola counties used iin these figures are FRANKLIN and WAKULLA.  
  
  
The State of Florida data are all of the counties, and this is selected in the FWC Commercial Fisheries Landings Summaries website.  


```{r landings_options setup, include=FALSE, warning=FALSE, message=FALSE, comment=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("cowplot")
library("devtools")
library("ggplot2")
library("ggpubr")
library("grid")
library("gridExtra")
library("lattice")
library("marelac")
library("scales")
library("ggpubr")
library("tidyverse")
```
  
```{r include=FALSE}

#Updated csv manually through FWC Commercial landings website
all_landings <- read.csv("data/oys_landings/landings_data.csv", header= T)

all_landings <- all_landings %>% 
  na.omit(value)


all_landings$area<- factor(all_landings $area,levels=c ("Apalachicola", "Suwannee Sound", "State"))
all_landings$value<- factor(all_landings$value,levels=c ("Landings (lbs)", "Total Trips", "CPUE"))

```
  
```{r echo= FALSE, fig.width= 6, fig.height= 8}
  ggplot(all_landings, aes(x= as.numeric(Year), y= as.numeric(measurement))) +
  geom_line (aes(color= area), size= 1.2) +
  geom_point(aes(color= area), size=3) +
  xlab("Year") +
  ylab("") +
  labs(color= "Area") +
  scale_linetype_manual(values = c('solid','dotted', 'longdash')) + 
  scale_color_manual(values= c("#0072B2", "#D55E00", "#CC79A7")) +
  scale_x_continuous (breaks= c(1986, 1987, 1988, 1989, 1990, 1991, 1992, 1993, 1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 2002, 2003, 2004, 2005, 2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014,2015, 2016, 2017,2018, 2019, 2020), labels= c(1986, "", 1988, "", 1990, "", 1992, "", 1994, "", 1996, "", 1998, "", 2000, "", 2002, "", 2004, "", 2006, "", 2008, "", 2010, "", 2012, "", 2014,"", 2016, "",2018, "", 2020)) +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme(legend.position = "top",
    axis.text.x = element_text(angle=90, hjust = 0.5), 
        panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"), 
        strip.text = element_text(size=15),
        text = element_text(size=15),
        axis.line = element_line(colour = "black"),
      panel.background = element_blank(),
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank()) +
  facet_wrap(~value , scales="free_y", ncol= 1) 
```
  
```{r echo=FALSE, fig.width= 6, fig.height= 8}
all_landings %>% 
  filter(Year > 2011) %>% 
  filter(!(area== "State")) %>% 
ggplot(aes(x= as.numeric(Year), y= as.numeric(measurement))) +
  geom_line (aes(color= area), size= 1.2) +
  geom_point(aes(color= area), size=3.5) +
  xlab("Year") +
  ylab("") +
  labs(color= "Area") +
  scale_linetype_manual(values = c('solid','dotted', 'longdash')) + 
  scale_color_manual(values= c("#0072B2", "#D55E00", "#CC79A7")) +
  scale_x_continuous (breaks= c(2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021)) +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme(legend.position = "top",
        axis.text.x = element_text(angle=90, hjust = 0), 
        panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"), 
        strip.text = element_text(size=15),
        text = element_text(size=15),
        axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  facet_wrap(~value , scales="free_y", ncol= 1) 

```

  
```{r, echo=FALSE, fig.width= 6, fig.height= 8}
all_landings %>% 
  filter(Year> 2014) %>% 
  filter(!(area== "State")) %>% 
  ggplot(aes(x= as.numeric(Year), y= as.numeric(measurement))) +
  geom_line (aes(color= area), size= 1.2) +
  geom_point(aes(color= area), size=3.5) +
  xlab("Year") +
  ylab("") +
  labs(color= "Area") +
  scale_linetype_manual(values = c('solid','dotted', 'longdash')) + 
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_color_manual(values= c("#0072B2", "#D55E00", "#CC79A7")) +
  scale_x_continuous (breaks= c(2015, 2016, 2017, 2018, 2019, 2020, 2021)) +
  #xlim(2015,2020) +
  theme(legend.position = "top",
        axis.text.x = element_text(angle=90, hjust = 1), 
        panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"), 
        strip.text = element_text(size=15),
        text = element_text(size=15),
        axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  facet_wrap(~value , scales="free_y", ncol= 1) 

```
  
```{r, echo=FALSE, fig.width= 6, fig.height= 8}
  all_landings %>% 
  filter(Year> 2014) %>% 
  filter(!(area== "State")) %>% 
  ggplot(aes(x= as.numeric(Year), y= as.numeric(measurement))) +
  geom_line (aes(color= area), size= 1.2) +
  geom_point(aes(color= area), size=3.5) +
  xlab("Year") +
  ylab("") +
  labs(color= "Area") +
  scale_linetype_manual(values = c('solid','dotted', 'longdash')) + 
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_color_manual(values= c("#0072B2", "#D55E00", "#CC79A7")) +
  scale_x_continuous(breaks= c(2015, 2016, 2017, 2018, 2019, 2020, 2021)) +
  #xlim(2015,2021) +
  theme(legend.position = "top",
        axis.text.x = element_text(angle=90, hjust = 1), 
        panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"), 
        strip.text = element_text(size=15),
        text = element_text(size=15),
        axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  facet_wrap(~value , scales="free_y", ncol= 1) 

```

